### 2024-01-05 paper/si_sections/3_others.tex
add si references

Section 3 Other additional information
Section 3.1 Additional information on machine learning environment.
The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system. The HyperBand algorithm [7], as implemented in KerasTuner [8] , facilitated the tuning process.

@@

The illustrations of CNN architecture displayed in Figure 1 of the main text, as well as  Supplementary Figure 21 and Supplementary Figure 30, were obtained from the GitHub repository dair-ai/ml-visuals [9]. Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.

>>>>

Section 3 Other additional information
Section 3.1 Additional information on machine learning environment.
The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system. The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.

@@

The illustrations of CNN architecture displayed in Figure 1 of the main text, as well as  Supplementary Figure 21 and Supplementary Figure 30, were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}. Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.
